Concurrent Programming in Harmony

### 2021-12-24 book/paper.tex
Proofread through Chapter 8

So far we have used Harmony to \emph{implement} various algorithms.
But Harmony can also be used to \emph{specify} what an algorithm is
supposed to do.
For example, \autoref{fig:lockspec} specifies the intended behavior
of a lock.
In this case, a lock is a boolean, initially <{False}>,
with two operations, \texttt{acquire()} and \texttt{release()}.
The \texttt{acquire()} operation waits until the lock is <{False}>
and then sets it to <{True}> in an atomic operation.
The \texttt{release()} operation sets the lock back to <{False}>.
The code is similar to \autoref{fig:naivelock}, except that waiting
for the lock to become available and taking it is executed as an
atomic operation.

@@

In Harmony, any statement can be preceded by the <{atomically}>
keyword.  It means that statement as a whole is to be executed atomically.
The <{atomically}> keyword can be used to specify the behavior of
methods such as \texttt{acquire} and \texttt{release}.  But
an actual executable program such as in \autoref{fig:cssynch} should not
use the <{atomically}> keyword.
In fact, if we want to make the entire program executable on hardware,
we have to also show how \texttt{Lock}, \texttt{acquire}, and \texttt{release}
are implemented, not just how they are specified.
\autoref{ch:spinlock} presents such an implementation.

@@

% In Harmony, atomic statements allow you to \emph{implement} your own
% atomic primitives such as test-and-set.  Other common examples
% include compare-and swap and fetch-and-add.
Atomic statements
are not intended to replace locks or other synchonization primitives.
When implementing synchronization solutions you should not directly use
atomic statements but use the synchronization primitives that are available
to you.  But if you want to \emph{specify} a new synchronization primitive,
then use \textbf{atomically} by all means.
You can also use atomic statements in your test code.
In fact, as mentioned before, \textbf{assert} statements are included to
test if certain conditions hold in every execution and are executed
atomically.

>>>>

So far, we have used Harmony to \emph{implement} various algorithms.
But Harmony can also be used to \emph{specify} what an algorithm is
supposed to do.
For example, \autoref{fig:lockspec} specifies the intended behavior
of a lock.
In this case, a lock is a boolean, initially <{False}>,
with two operations, \texttt{acquire()} and \texttt{release()}.
The \texttt{acquire()} operation waits until the lock is <{False}>
and then sets it to <{True}> in an atomic operation.
The \texttt{release()} operation sets the lock back to <{False}>.
The code is similar to \autoref{fig:naivelock}, except that waiting
for the lock to become available and taking it is executed as an
atomic operation.

@@

In Harmony, any statement can be preceded by the <{atomically}>
keyword.  It means that statement as a whole is to be executed atomically.
The <{atomically}> keyword can be used to specify the behavior of
methods such as \texttt{acquire} and \texttt{release}.  But
an actual executable program---such as the one in
\autoref{fig:cssynch}---should not use the <{atomically}> keyword
because---on a normal machine---it cannot be directly compiled into
machine code.
If we want to make the program executable on hardware,
we have to show how \texttt{Lock}, \texttt{acquire}, and \texttt{release}
are implemented, not just how they are specified.
\autoref{ch:spinlock} presents such an implementation.

@@

% In Harmony, atomic statements allow you to \emph{implement} your own
% atomic primitives such as test-and-set.  Other common examples
% include compare-and swap and fetch-and-add.
Atomic statements
are not intended to replace locks or other synchonization primitives.
When implementing synchronization solutions you should not directly use
atomic statements but use the synchronization primitives that are available
to you.  But if you want to \emph{specify} a synchronization primitive,
then use \textbf{atomically} by all means.
You can also use atomic statements in your test code.
In fact, as mentioned before, \textbf{assert} statements are included to
test if certain conditions hold in every execution and are executed
atomically.
